Nail: A practical interface generator for binary formats

### 2014-04-01 paper/intro.tex
turn Boost.Spirit into a citation

Third, applications often need to produce output in the same
format as their input---for example, applications might both
read and write files, or both receive and send network packets.
Most parser generators just focus on parsing an input, rather
than producing an output, thus requiring the programmer to manually
construct outputs, which is error-prone.  Some parser generators, such as
Boost.Spirit,\footnote{\url{http://www.boost.org/doc/libs/1_55_0/libs/spirit/doc/html/index.html}}
allow reusing the grammar for generating output from the internal
representation.  However, those generators require yet another set of
semantic actions to be written, transforming the internal representation
into an AST\@.

>>>>

Third, applications often need to produce output in the same
format as their input---for example, applications might both
read and write files, or both receive and send network packets.
Most parser generators just focus on parsing an input, rather
than producing an output, thus requiring the programmer to manually
construct outputs, which is error-prone.  Some parser generators, such as
Boost.Spirit~\cite{boost-spirit},
allow reusing the grammar for generating output from the internal
representation.  However, those generators require yet another set of
semantic actions to be written, transforming the internal representation
into an AST\@.
